Solar wind, F10.7, and geomagnetic activity relationship to the equatorial plasma mass density at geosynchronous orbit

### 2016-10-19 paper/paper.template.tex
Now with table included

\begin{keypoints}
\item = enter point 1 here = 
\item = enter point 2 here = 
\item = enter point 3 here = 
\end{keypoints}

@@

\begin{table}
	\small
	\centering
	\input{../tables/DeltaBootstraps-case10.txt}
	\caption{Results of test on of medians of $\rho_{eq}$ shown in the top panel of Figure~\ref{fig:DailyAveragedDstEvents} between days of threshold crossing  near (day = 1 or -1) or on the day of a $D_{st}$ event (day = 0).}
	\label{BootstrapDifferenceTable}
\end{table}

>>>>

\begin{keypoints}
\item Hourly averages are required to show a statistically significant mass density response during high geomagnetic activity

\item The response of mass density for high geomagnetic activity intervals is strongest when F10.7 is elevated

\item There is no solar wind variation signature associated with large mass density events 
\end{keypoints}

@@

\begin{table}
	\small
	\centering
	\begin{tabular}{|c|cc|}
		\hline 
		Days & Difference (amu/cm$^3$) & \%  \\ \hline
		-1 0 & -4.48 & $10.90\%\geq 0$  \\ 
		-1 1 & -1.46 & $34.30\%\geq 0$  \\ 
		1 0 & -3.02 & $21.50\%\geq 0$  \\ 
		\hline
	\end{tabular}
	\caption{Results of test on of medians of $\rho_{eq}$ shown in the top panel of Figure~\ref{fig:DailyAveragedDstEvents} between days of threshold crossing  near (day = 1 or -1) or on the day of a $D_{st}$ event (day = 0).}
	\label{BootstrapDifferenceTable}
\end{table}
